%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {MadByte Games} % Organization
    {Istanbul, Turkey} % Location
    {Mar. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Participated in core team due to ability to high availability, scalability, improving development and deployment processes}
        \item {Provided user requirements analysis, design, programming and documentation support for enhancement of Web API application accessed by 30 million registered and 250k daily player worldwide}
        \item {Managed big data transfer from MSSQL to BigQuery. Scheduled retroactive and daily (approximated 2 million) data transfers}
        \item {Automated ETL processes, making it easier to wrangle data and reducing time by as much as 40\%.}
        \item {Identified performance issues that could be improved through load tests. Investigating, diagnosing and correcting system issues}
        \item {Skills Used: C\#, .NET Core, Python, Bash, Web API, WebSocket, RabbitMQ, Google Cloud, Docker, Apache Airflow, Svn, Git, Swagger}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Radity (Remote)} % Organization
    {Zürich, Switzerland} % Location
    {Sep. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed RESTful API using .NET Core framework with reusable and maintainable code}
        \item {Performed relational database schema and data migrations between environments}
        \item {Worked closely with designer for requirements in application interface}
        \item {Built the integration test process and wrote test scenarios using the Chai Assertion Library}
        \item {Managed build and deployment process with Azure cloud service}
        \item {Skills Used: C\#, .NET Core, Web API, Vue.js, TypeScript, Entity Framework, LINQ, SQL Server, SQLite, RESTful, JSON, Azure, Git, Postman, Swagger}
        % \item {Provisioned an easily managable hybrid infrastructure(Amazon AWS + On-premise) utilizing IaC(Infrastructure as Code) tools like Ansible, Packer and Terraform.}
        % \item {Built fully automated CI/CD pipelines on CircleCI for containerized applications using Docker, AWS ECR and Rancher.}
        % \item {Designed an overall service architecture and pipelines of the Machine Learning based Fashion Tagging API SaaS product with the micro-services architecture.}
        % \item {Implemented several API microservices in Node.js Koa and in the serverless AWS Lambda functions.}
        % \item {Deployed a centralized logging environment(ELK, Filebeat, CloudWatch, S3) which gather log data from docker containers and AWS resources.}
        % \item {Deployed a centralized monitoring environment(Grafana, InfluxDB, CollectD) which gather system metrics as well as docker run-time metrics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Developer} % Job title
    {Projet Yazilim} % Organization
    {Istanbul, Turkey} % Location
    {Sep. 2015 - Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as full stack developer with followed by Scrum methodologies}
        \item {Developed and maintained in exist enterprise business solutions}
        \item {Developed addons on suite of business apps that covers all enterprise management needs in Odoo}
        \item {Implemented several ERP web services integration (such as SAP, Odoo)}
        \item {Developed web api is built to be as interface for clients who wants to integrate with their data to our solutions}
        \item {Optimized back-end logic to avoid performance issues in legacy projects for example i decreased many page load issue with query optimization and using pagination}
        % \item {I had responsible for server management and configurations included on-premise customers}
        \item {Gained experience with many local bank integrations and payment gateway APIs}
        \item {Skills Used: C\#, Python, ASP.NET Webform/MVC, TSQL, Entity Framework, jQuery, RESTful, SOAP, XML-RPC, XML, JSON, Kendo UI, TFS, Git, JIRA}
        % \item {Implemented RESTful API server for car rental booking application(CARPLAT in Google Play).}
        % \item {Built and deployed overall service infrastructure utilizing Docker container, CircleCI, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        % \item {Developed an easy-to-use Payment module which connects to major PG(Payment Gateway) companies in Korea.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Basar Bilisim} % Organization
    {Istanbul, Turkey} % Location
    {Dec. 2014 - Jun. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed enhancements to CRM/SPA solutions and services}
        \item {Assisted in the full life-cycle for the development of new functionality, including analysis work, prioritizing, coding, testing and production rollout and post-implementation}
        \item {Worked interactively with the team and end users to resolve any issues that occurred}
        \item {Skills Used: C\#, ASP.NET MVC, LINQ, SQL, Entity Framework, AngularJS, JavaScript, jQuery, AJAX, Bootstrap, HTML5, CSS3, Visual SVN}
        % \item {Lead engineer on agent-less backtracking system that can discover client device's fingerprint(including public and private IP) independently of the Proxy, VPN and NAT.}
        % \item {Implemented a military cooperation system which is web based real time messenger in Scala on Lift.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Astajans Adworks} % Organization
    {Istanbul, Turkey} % Location
    {Apr. 2014 - Oct. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Building web applications, cms and e-commerce solutions, responsible for hosting services for the customers.}
        \item {Skills Used: ASP, PHP, MySQL, jQuery, HTML/CSS, Wordpress, Opencart}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Freelance Web Developer} % Job title
  %   {Self-Employed} % Organization
  %   {Istanbul, TR} % Location
  %   {Jan. 2010 - Aug. 2012} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {I worked on some smaller web projects. I used .NET/C\# ASP.NET MVC and other Microsoft based technologies.}
  %       % \item {Developed a proxy drive smartphone application which connects proxy driver and customer.}
  %       % \item {Implemented overall Android application logic and wrote API server for community service, along with lead engineer who designed bidding protocol on raw socket and implemented API server for bidding.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
